Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-09-22 paper/main.tex
add note about viewing all top-level attribute values via davos.config

\bigskip\bigskip\textcolor{red}{\textbf{========== TODO: finish editing from here to end ==========}}\bigskip\bigskip

@@

%- .require_pip()
\item \texttt{require\_pip(version\_spec, warn=False, extra\_msg=None, prereleases=None)}:
%- .require_python()
\item \texttt{require\_python(version\_spec, warn=False, extra\_msg=None, prereleases=None)}:
%- .use_default_project()
\item \texttt{use\_default\_project()}:
\end{itemize}

>>>>

The current values of all \texttt{davos} attributes may be viewed at once within a notebook by displaying the \texttt{davos.config} object.

@@

%- .require_pip()
%\item \texttt{require\_pip(version\_spec, warn=False, extra\_msg=None, prereleases=None)}:
%- .require_python()
\item \texttt{require\_python(version\_spec, warn=False, extra\_msg=None, prereleases=None)}:
%- .use_default_project()
\item \texttt{use\_default\_project()}:
\end{itemize}
